A semantics of core AUTOSAR

### 2016-08-01 paper/paper.tex
Added equation numbering.
Dump.

@@

@@

\subsection{Exclusive areas}
\[ \begin{array}{r@{}c@{}l}      \ExclusiveAreas          \end{array} \]
\subsection{Inter-runnable variables}
\[ \begin{array}{r@{}c@{}l}      \InterrunnableVariables  \end{array} \]
\subsection{Sending/receiving}
\[ \begin{array}{r@{}c@{}l}      \SendingReceiving        \end{array} \]
%TODO: RuleLong?
\subsection{Reading/writing (unbuffered versions of rcv and snd)}
\[ \begin{array}{r@{}c@{}lcl}    \ReadingWriting          \end{array} \]
\subsection{Calling a server}

\renewcommand\Pcomma{\\&&\text{and}\;\;}

\[ \begin{array}{r@{}c@{}lcl}    \CallServer              \end{array} \]
\subsection{Passing back a server result}
\[ \begin{array}{r@{}c@{}lcl}    \ServerResult            \end{array} \]
\subsection{Spawning and terminating}
\[ \begin{array}{r@{}c@{}lcl}    \SpawnTerminate          \end{array} \]
\subsection{Passing time}
\[ \begin{array}{r@{}c@{}lcl}    \PassingTime             \end{array} \]
\subsection{Ignoring broadcasts}
{
\renewcommand{\Prule}[2]{#1 & \Pif \;\; #2\\}
\[ \begin{array}{r@{}c@{}lcll}    \IgnoreBroadcast         \end{array} \]
}

>>>>

The AUTOSAR naming scheme guarantees that all processes terms in such an initial composition will carry unique addresses, with exception of timer terms which share addresses with the runnables they belong to. We will later see how runnable instances reuse the address of their runnables in the same manner.

@@

An exclusive area is the analogue of a binary semaphore, that can be acquired and released in an atomic fashion by competing runnable instances. Rule (1) states that a runnable instance executing $\Enter x k$ may successfully proceed to executing its continuation $k$ by broadcasting $\say{\Tx x i}{\Tenter}$ to its process environment. Rule (3) expresses that exclusive area $\Tx x i$ accepts hearing $\hear{\Tx x i}{\Tenter}$ if it is currently not taken; i.e., carries the boolean state $\Tfalse$. This makes it possible for a runnable instance and an exclusive area term to engage in a parallel transition:
\begin{eqnarray}
	\Tstep{\TparLong{\Trinst{\Tr{\Tvar{R}}{\Tvar{I}}}{\Tvar{C}}{\Tvar{Xs}}{\TrteEnter{\Tvar{X}}{\Tvar{K}}}}
				{\Texcl{\Tx{\Tvar{X}}{\Tvar{I}}}{\Tfalse}}}
	  	  {\say{\Tx x i}{\Tenter}}
		  {\TparLong{\Trinst{\Tr{\Tvar{R}}{\Tvar{I}}}{\Tvar{C}}{\Tcons{\Tvar{X}}{\Tvar{Xs}}}{\Tap{\Tvar{K}}{\Tok}}}
		  {\Texcl{\Tx{\Tvar{X}}{\Tvar{I}}}{\Ttrue}}}
\end{eqnarray}

@@

\subsection{Exclusive areas}
\begin{eqnarray}      \ExclusiveAreas          \notag \end{eqnarray}

\subsection{Inter-runnable variables}
\begin{eqnarray}      \InterrunnableVariables  \notag \end{eqnarray}

\subsection{Sending/receiving}
\begin{eqnarray}      \SendingReceiving        \notag \end{eqnarray}

%TODO: RuleLong?
\subsection{Reading/writing (unbuffered versions of rcv and snd)}
\begin{eqnarray}      \ReadingWriting          \notag \end{eqnarray}

\subsection{Calling a server}

\renewcommand\Pcomma{\nonumber \\&&\text{and}\;\;}

\begin{eqnarray}      \CallServer              \notag \end{eqnarray}

\subsection{Passing back a server result}
\begin{eqnarray}      \ServerResult            \notag \end{eqnarray}

\subsection{Spawning and terminating}
\begin{eqnarray}      \SpawnTerminate          \notag \end{eqnarray}

\subsection{Passing time}
\begin{eqnarray}      \PassingTime             \notag \end{eqnarray}

%\renewcommand{\Prule}[2]{#1 & \Pif \;\; #2\\}
\subsection{Ignoring broadcasts}
\begin{eqnarray}      \IgnoreBroadcast         \notag \end{eqnarray}
